Assignment 4

### 2015-03-10 rmtw/a4/latex8.tex
stdio

\Section{Methodology}
This section will describe which statistical tests were used, and why. The level of significance used for all tests is 0.05.

@@

\begin{table}
	\centering
	\begin{tabular}[Ht]{| l | l | l | l |}
	\hline
	 & A Faults & B Faults & C Faults  \\
	\hline
	Group A & 36 & 40 & 35 \\
	\hline
	Group B & 31 & 47 & 28 \\
	\hline
	\end{tabular}
	\caption{Fault frequency of risk type per group}
\end{table}

\Section{Results}
This section will cover the results of the experiment.

\subsection{Efficiency and Effectiveness A}
Since the data is non-normalised, the Wilcoxon-Mann-Whitney (WMW) two-sample rank-sum test was chosen instead of the Student's T-test as the final test. The data used for the WMW test was the efficiency of each participant. The result of the WMW test was W=250, p=0.1063 and with the significance level of 536, thus the null hypothesis H\textsubscript{0} Eff is rejected.

The results of the study show some interesting results. The rejection of \textsubscript{0} Eff indicates that there is a difference between the efficiency of the inspection methods.

\subsection{Efficiency and Effectiveness B}
The same test was chosen for Hrate, based on the same reasoning. The result of the WMW test for Hrate was W=250, p=0.1063 and with the significance level of 536 thus the null hypothesis H\textsubscript{0} Rate is rejected.

\subsection{Results for H\textsubscript{Fault}}
As mentioned previously, the CS test was used to determine if the reviewers discovered the same frequency of results. The result of the X\textsubscript{2} was 1.5998, generating a p-value of 0.4494. For v=2 and alpha = 0.05, the upper critical value is 5.991 and the lower critical value is 0.103. Since 1.5998 is \textless 5.991 and \textgreater 0.103, the alternative hypothesis of the CS test is rejected. Since \textsubscript{0 Fault} and \textsubscript{1 Fault} are inverted compared to the hypothesis of the CS test, the null hypothesis of H\textsubscript{Fault} is rejected.

@@

\begin{table}
	\centering
	\begin{tabular}[Ht]{|l|l|l|}
	\hline
	& UC & CL \\
	\hline
	Mean(Total faults found) & 4.61 & 5.48 \\
	\hline
	Median(Total faults found) & 3.5 & 5.0 \\
	\hline
	Detection Rate & 0.12 & 0.14 \\
	\hline
	A Faults & 36 & 31 \\
	\hline
	B Faults & 40 & 47 \\
	\hline
	C Faults & 35 & 20 \\
	\hline
	\end{tabular}
	\caption{Results Summary}
\end{table}

>>>>

\Section{Methodology}
This section will describe which statistical tests were used, and why. The level of significance used for all tests is 0.05. The results have been analysed using a descriptive approach together with a statistical approach.

@@

\begin{table}
	\centering
	\begin{tabular}[ht]{| l | l | l | l |}
	\hline
	 & A Faults & B Faults & C Faults  \\
	\hline
	Group A & 36 & 40 & 35 \\
	\hline
	Group B & 31 & 47 & 28 \\
	\hline
	\end{tabular}
	\caption{Fault frequency of risk type per group}
\end{table}

\Section{Results}
This section will cover the results of the experiment. The results for H\textsubscript{Eff} and H\textsubscript{Rate} are described in the same sub-sections, since the results are similar and since the results both are relative to the number of average faults found.

\subsection{Results for H\textsubscript{Eff} and H\textsubscript{Rate}}
Since the data is non-normalised, the Wilcoxon-Mann-Whitney (WMW) two-sample rank-sum test was chosen instead of the Student's T-test as the final test. The data used for the WMW test was the efficiency of each participant. The result of the WMW test was W=250, p=0.1063 and with the significance level of 536, thus the null hypothesis H\textsubscript{0 Eff} is rejected.

The same test was chosen for H\textsubscript{Rate}, based on the same reasoning. The result of the WMW test for H\textsubscript{Rate} was W=250, p=0.1063 and with the significance level of 536 thus the null hypothesis H\textsubscript{0 Rate} is rejected.

As evident from the tests, and as can be seen in Table 4, the results for H\textsubscript{Eff} and H\textsubscript{Rate} are similar. Both show that there is a difference between the two inspection methods, and both show greater results for CL.

%% ctrl+F for "exactly  and why one inspection process"

\subsection{Results for H\textsubscript{Fault}}
As mentioned previously, the CS test was used to determine if the reviewers discovered the same frequency of results. The result of the X\textsuperscript{2} was 1.5998, generating a p-value of 0.4494. For v=2 and alpha = 0.05, the upper critical value is 5.991 and the lower critical value is 0.103. Since 1.5998 is \textless 5.991 and \textgreater 0.103, the alternative hypothesis of the CS test is rejected. Since \textsubscript{0 Fault} and \textsubscript{1 Fault} are inverted compared to the hypothesis of the CS test, the null hypothesis of H\textsubscript{Fault} is rejected.

@@

\begin{table}
	\centering
	\begin{tabular}[ht]{|l|l|l|}
	\hline
	& UC & CL \\
	\hline
	Mean(Total faults found) & 4.61 & 5.48 \\
	\hline
	Median(Total faults found) & 3.5 & 5.0 \\
	\hline
	Detection Rate & 0.12 & 0.14 \\
	\hline
	\end{tabular}
	\caption{Results Summary}
\end{table}
